---
title: "HW1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

## Read the data 
```{r import_Data}
HW1_data=
  read_csv(file="./data/HW2dat.csv")
```
install.packages("psych")
install.packages("GPArotation")

```{r install_packages}
library(psych)
library(GPArotation)
```

###descriptive statistics 
```{r}
summary(HW1_data)
```

### adds the data so variable names can be used without pre-specificaiton of data names
```{r}
attach(HW1_data)
```

## Question 1: Obtain eigenvalues and scree plot associated with the Pearson Correlation matrix of the 5 items 

###create an object with just the variables we want to analyze
```{r}
usevars_1<-cbind(C1, C2, C3, C4, C5)
```
### Using Pearson Correlation
```{r}
HW1parallel_pearson<-fa.parallel(usevars_1)
str(HW1parallel_pearson)
HW1parallel_pearson$pc.values
#HW1parallel_pearson$pc.sim$mean
```
### Question 2: Report the internal consistency associated with simple sum 
###Using polychoric correlation and do parallel anlaysis of eigenvalues

```{r}
usevars_2<-cbind(C1, C2, C3, C4_R, C5_R)
```

### cronbach's alpha
```{r}
HW1alpha<- alpha(usevars_2)
HW1alpha
```
# Question 3: 
```{r}
HW1alpha<- alpha(usevars_1)
HW1alpha
```
```{r}
usevars_3<-cbind(C1, C2, C3)
HW1alpha<- alpha(usevars_3)
HW1alpha
```
